Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-18 forecast/paper/supplement.tex

\author{Daniel J.\ McDonald, Jacob Bien, Alden Green, Addison Hu, Nat DeFries, Sangwon Hyun, Natalia L.\ Oliveira, James Sharpnack, Jingjing Tan, Robert Tibshirani, Valerie Ventura, Larry Wasserman, and Ryan J.\ Tibshirani}
\correspondingauthor{Daniel J. McDonald.\\E-mail: daniel@stat.ubc.ca}

>>>>

\author{Daniel J.\ McDonald, Jacob Bien, Alden Green, Addison Hu, Nat DeFries, Sangwon Hyun, Natalia L.\ Oliveira, James Sharpnack, Jingjing Tang, Robert Tibshirani, Valerie Ventura, Larry Wasserman, and Ryan J.\ Tibshirani}
\correspondingauthor{Daniel J. McDonald.\\E-mail: daniel@stat.ubc.ca}
